\documentclass[11pt]{article}
\pagestyle{plain} \topmargin -.5in \oddsidemargin 0in
\evensidemargin 0in \textwidth 6.5in \textheight 8in
\setlength{\parindent}{0in}
\title{Silent Auction Donation Packet}
\author{SERV Auction 2016}
\date{November 7th, 2016 to November 11th, 2016}
\begin{document}
\maketitle
\section{Services}
\subsection{Over-Analyze Comedy}
Bill Wong (William.wong@students.olin.edu) \\
Starting Bid: \$0 \\
Winner(s): 
Top bidder\newline
Show me some comedy in any form (video, picture, text) and I'll over-explain why it's funny and how you could be funny in the same way.
\subsection{Personal Hype Man}
Alexander Li (alexander.li@students.olin.edu) \\
Starting Bid: \$0.001 \\
Winner(s): 
Top bidder\newline
I'll be your hype man for like a day. Idk.
\subsection{Day of Puns}
Nicholas Sherman (Nicholas.Sherman@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
I will send you every pun I make in a 24 hour period. Yes, EVERY pun. This is to also make up for all the puns I will miss out on next year.
\subsection{1 Hr of Unqualified Advice}
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
I will give you advice on anything you want for an hour. I am completely unqualified and you should take all my advice with a massive grain of salt. There were also be refreshments of your choice for bids over \$10. Groups are allowed just make sure the bid reflects it. The session may also run long if necessary.
\subsection{Set up your website}
Lydia Zuehsow (Lydia.Zuehsow@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
Get the website (or online portfolio!) of your dreams, with none of the pain.
You bring the idea, I handle the annoying backend DNS rerouting and URL setup.

If bidding on this item goes above \$20, I will write you a one page website with a generic CSS graphical style template of your choice.
For every additional \$20 after that, I will write and link an additional HTML page with the content of your choice to your main homepage.
If bidding tops \$100, you can choose whether I attempt to integrate an opensource API of your choice (PayPal, Facebook, etc.) or customize your website design (Custom CSS stylesheet)
\subsection{Anything in the SERV Auction}
Aaron Greiner, Patrick Huston (aaron.greiner@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
You pick the SERV Auction item, we will do our best* to re-create it.

*Our effort to re-create it will depend on how much money you give, the more you give, the better we try.
\subsection{"Explaining" Things}
Sophie Schaffer and Siena Okuno (Sophie.Schaffer.and.Siena.Okuno@students.olin.edu) \\
Starting Bid: \$0.25 \\
Winner(s): 
Top bidder\newline
Got something you want to know more about? We can try to tell you! Do we actually know anything about this topic? Probably not, but we will try our darndest.
\subsection{Pinot NURoir}
Linnea Laux and Sara Ballantyne (linnea.laux@students.olin.edu) \\
Starting Bid: \$0.5 \\
Winner(s): 
Top bidder\newline
We will provide you an appropriate grapey beverage and facilitate an opportunity to view a Noir film with Nur.
\subsection{"Crisp" High Five}
Cusai (cusai@students.olin.edu) \\
Starting Bid: \$0.99 \\
Winner(s): 
Top 7 bids\newline
Self explanatory
\subsection{POMES}
Clur (clairekincaid98@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top 9000 bids\newline
my naym is clur
an I liyk rime
an if yu wan
a rimy tiym
then bid on dis
wil follo yu
an mayk up riyms
on wat yu do

or if yu ar
a trol liyk me
chuz somwan elz
an yu wil see
I follo dem 
an mayk up rime
on wat they do
yu have fun time
\subsection{Take You on an Adventure}
Rowan \& Toby (rowan.sharman@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
(\$)/(Party Size) = |Adventure|
\subsection{Unfiltered Criticism}
Lydia Zuehsow (Lydia.Zuehsow@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will tell you why your idea sucks.
\subsection{Comment your Code}
Justin Kunimune (Justin.Kunimune@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will interpret and add comments to up to 1000 lines of code that you send me in any language. I know Java, Python, MatLab, Javascript, C, Arduino, and Labview, so my comments will probably be of higher quality in those than, say, Ruby.
\subsection{Draw you a Picture in Latex}
Justin Kunimune (Justin.Kunimune@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will concoct a diagram or image of your choosing in Latex code, and give you both the compiled pdf and source tex.
\subsection{Hot beverages and real talk}
Sophia Nielsen (sophia.nielsen@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
For the low low price of whatever you bid I will prepare the hot beverage of your choosing and give you my unfiltered opinion on anything. Great bonding experience. No person limit
\subsection{Shitty Poster!}
Aaron, Annabel, and Keenan (keenan.zucker@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
We do design things! So we will purposely go against all of our best instincts and judgements to create the shittiest, awful, yet glorious poster you can imagine. It will be bad. You definitely won't like it. But we will have fun making it. Please humor us. It can be for an event, room decoration, or to burn forever!
\subsection{Expensive Hug}
Liz Leadley (liz@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 2500 bids\newline
Finally, a hug that isn't free! The same quality hug as Free Hug Friday hugs, but I'll make a minor effort to track you down to hug you.
Hugs are basically infinite, so everyone who bids wins. Bidding multiple times wins multiple separate hugs.
\subsection{One Hug}
Tommy Weir (tommy.weir@...) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
One hug, that's it
\subsection{And now, Wonderwall}
Andrew Deaver \& Jeff Pfleuger (Andrew.Deaver@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Jeff plays banjo. Andrew plays guitar. We know this because they can both play Wonderwall. Everyone loves Wonderwall. But everyone loves watching their friends suffer as Jeff and Andrew relentlessly serenade them with only Wonderwall more. Buy this item and we'll relentlessly serenade a person of your choosing. Every \$3 past the initial bid will get your friends (or enemies) one more rendition of Wonderwall. The more money, the better (or worse) it'll be.
\subsection{Play Forza 7 with me}
Sreekanth (sreekanth.sajjala@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 5 bids\newline
Get to play forza 7 with me on my xbox with me whenever I am free.
\subsection{I will laser cut you something cool}
Jeff Pflueger (jeff@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
As a laser ninja, i spend a lot of time laser cutting. If you win this auction item, I will spend some of that time cutting something specifically for you! The higher this auction item goes, the longer i will spend on your cool thing!
\subsection{Makeover with Lauren}
Lauren Pudvan (Lauren.Pudvan@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 2 bids\newline
As most of you know, I really enjoy expressing creativity through make-up and hair. Let me be creative with you and I will do your hair and make-up however you want. (I can also teach you how I do what I do!)
\subsection{Take you on an Adventure!}
Chloe Grubb (chloe.grubb@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I enjoy getting off campus. I also enjoy finding interesting things to do while off campus. So, if you want to get in on some of the shenanigans, bid on this! 
*Note: Level of shenanigans correlate to the amount of the bid.
\subsection{Advice on how to live in a van}
Brennan VandenHoek (Brennan@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
I spent the last 8 months living out of a van in Silicon Valley. As a now expert on the subject I will give you advice on how to navigate the ins and out of van life
\subsection{Watch Broad City with Us}
Aaron Greiner, Annabel Consilvio (annabel@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
FOUR AND THREE AND TWO AND ONE ONE
\subsection{Learn to be sarcastic like me}
Kevin Crispie (kevin.crispie@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Someone once told me I tend to be a sarcastic person. I want to share that goodness and cheer with the world. I’ll teach the ways of a sarcasm master to you and possibly a group of friends, instructing you how to have just as sick of a mind as I do. Want to bring some sardonic cheer to your team meeting? I’ll sit in and make sarcastic yet entertaining comments about your project. If you buy this item, we’ll go on a perilous journey together to the sacred and remote mountain shrine where I learned to be such a pure and enlightened person.
\subsection{Mechanical Engineering Private Help}
Kevin Crispie (kevin.crispie@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I’ll open the wide world of mechanical engineering to you. I can teach you FEA in ANSYS, composites fabrication, Mech Solids wizardry, Dynamics, or how rockets work (subject to me making sure I don’t violate my SpaceX NDA). Want to make sure what you make doesn’t break? I’ll teach you about material selection and failure analysis. Need help preparing for a technical interview or need a resume review? I got you. Can’t decide on what to do? We’ll pick a few at random. I’ll give an amount of time proportional to your bid. Open to up to 5 people, though this can be negotiated.
\subsection{Life advice from an alum}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Maybe you know me, and maybe you don't. I graduated from Olin in 2014 and worked in the Admission office for a year. I know that I don't know anything, and I reckon that won't get in the way of somebody bidding on this item.
You win, we chat. I learn about your situation and tell you what I think. You get my best advice no matter the bid... but if you bid big, you'd better hold onto your hat!
\subsection{Visit me in Vancouver, Canada!}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Vancouver is beautiful, and you should consider visiting. If you do, let me know! I'll take you around. Depending on how high the bidding gets, I will concierge for you... host you... bring you around town... drive you to mountains, rivers, or other adventures... host a gala in your honour... the sky is the limit!
\subsection{I will spend \$100 if your money for you}
Brennan VandenHoek (Brennan@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will spend \$100 of your money on something that you absolutely need but didn’t know that you needed. I am very good a buying things and making money go far. So I promise it will be great! 

We will sit down and have a chat. It will be like reading your fortune but more expensive and more likely to actually help you. Plus you will get mailbox surprises!
\subsection{Manik Therapy Session}
Manik (Manik@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
I've been told I actually have decent therapy skills and I give good life advice. There will be none of that here, however. Bring 2 friends, or 3, or whatever, and tell me all the problems you all have. I will try my hardest to give you the worst advice I can. You will leave in worse shape than you were when you came in. This worked pretty well last year so we're back for round two.
\subsection{What is grad school!? Chat with PhD Student about all your questions!}
Jamie Gorson (jgorson@northwestern.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
I am now in my 2nd year of my PhD. Before starting and while at Olin, I had no idea what grad school would be like and entail. I'm happy to skype with someone and talk about grad school, whether if you are applying now, looking at fellowships, or thinking about it for the future. If you're in Chicago at some point we can chat in person.
\subsection{Build you a robot}
Connor Novak (connor.@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I will build you a robot! The amount of time that I spend on the robot is proportional to the amount of money you pay. The robot has the potential of being amazing. Ask Katya.
\subsection{2 hrs of Mech-E work }
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I will do mechanical work for a project of your choice. This work can be simulation, design, or fabrication.
\subsection{Fancy Manicure}
Siena Okuno (siena.okuno@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I've got stamps, nail strips, glitter, holographic glitter, stickers, and everything else! Send in a fancy nail design and I will recreate it on your nails.
\subsection{Makeover}
Isabel Blancett and Lacie Fradet (Isabel.Blancett.and.Lacie.Fradet@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 2 bids\newline
Isa and Lacie will do your hair and/or makeup for an event of your choosing.
\subsection{Compilation of favorite comedian bits}
Emily Lepert (Emily.Lepert@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 2 bids\newline
I will compile my favorite Jon Stewart, John Oliver, and The Daily Show clips/bits and send them to you for your enjoyment.
\subsection{Logo of YOUR FACE}
Keenan Zucker (keenan.zucker@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I will design a icon of YOUR FACE! That's right, YOU! It's gonna be your face, vectorized! Use it for things like personal websites or impressing that special someone. You can send me a couple photos of yourself, or let me decide the photo of you (not recommended)
\subsection{Spa Day}
Celina Bekins (Celina.Bekins@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
We'll schedule a day together of chatting, drinking tea, listening to music - whatever you find relaxing. Lomi lomi massage included, and if you want your hair cut our dyed that can happen too. Basically it's a day for pampering. Treat yourself.
\subsection{Knitting Lessons}
Anna Griffin and Daniel Connolly (anna.griffin@students.olin.edu; daniel.connolly@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 3 bids\newline
Knitting lessons with Daniel and Anna
\subsection{Advice on used car buying}
Brennan (Brennan@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I will give you advice/help you in purchasing a used car. Over \$20 and I will go with you to look at a car
\subsection{I Ching reading}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top 2 bids\newline
For the past two years I have been using a system called the I Ching to think about questions in my life both big and small. I estimate that I have also done about 200 divinations for friends and strangers in that time, helping guide them towards how to approach challenging situations using a balance of receptive yin and active yang energy.
This item includes a Skype call, introduction/catch up conversation, explanation about how the I Ching works, and divination session. 1-2 hours, satisfaction guaranteed!
\subsection{2 Practice Software Interviews}
Shane Skikne (ShaneSkikne@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
I've done many software interviews from both sides. I'll interview you twice and provide detailed feedback after each.
\subsection{You r Body ART}
Izzy Harrison, Frankie Devanbu (izzy@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
We will make you into an amazing piece of art. Feathers, Paint, Bling, Adhesive Velvet- nothing is too good for you. We will work together to realize our combined vision. Photography included. Nude is natural- but not required.
\subsection{Knife Sharpening}
Aiden Carley-Clopton (aiden.carley-clopton@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 3 bids\newline
I will sharpen your knives for you and show you how to do it so you can keep them sharp
\subsection{Get Added to Our Photo Wall}
Backsuiteish Boys ft. ABBA (patrick.huston@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
We've got a pretty great photo wall going, and you can be a part of it. Flannel shirt provided.
\subsection{Make you be less lazy}
Maximilian Schommer (maximilian.schommer@students.olin.edu) \\
Starting Bid: \$15 \\
Winner(s): 
Top bidder\newline
Lets be real, you're pretty lazy. You've always had this one project you've never done because you haven't been able to motivate yourself to do it. Or you've always wanted to get up earlier or work out more or practice that instrument that you've pretty much never played since high school. Well sometimes you only have so much willpower, and you need a little, or very big push to get you moving. 

That's what I'm for! I'll bother you on messenger, walk into your room and wake you up, drag you to the gym, send an all students to find you, slap you in the face, or whatever it takes to help you do that thing that you just need a bit of extrinsic motivation to achieve. Bid is for one month of such a service, and every \$50 will add an additional month.

P.S. Face slapping is optional.
\subsection{Shovel Your Car Out (at Olin)}
Walker Trelease (walker@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 2 bids\newline
In a few months your car will be regularly trapped by snow. We can fix that for you. First shovel for starting bid, +1 for each additional \$10.
\subsection{Roommate for 12 hours}
CJ (CJ@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
CUSAI will accompany you to do whatever you would like on a day of your choice. No heavy lifting.
\subsection{A Tour of my Homemade Mobile Tiny House}
Maya Calabria (maya.calabria@students.olin.edu) \\
Starting Bid: \$50 \\
Winner(s): 
Top 5 bids\newline
I designed and built a tiny house over this summer from scratch. I'd love to give you a tour of my project and give you a taste for tiny living. Calling all sustainability geeks!!!
\subsection{Forge Workshop}
Claire  (clairekincaid98@gmail.com) \\
Starting Bid: \$80 \\
Winner(s): 
Top 4 bids\newline
Basic Ornamental Blacksmithing Workshop on Olin's Forge.  Approximately 4-5 hours.  Maximum of 4 people in the workshop.  You walk away from the workshop officially trained on the forge and get to keep your thing that you made in the workshop.
\section{Food}
\subsection{Make and Decorate Cake Pops with Me}
Zarin Bhuiyan (Zarin.Bhuiyan@students.olin.edu) \\
Starting Bid: \$0.5 \\
Winner(s): 
Top 2 bids\newline
I'm making cake pops as part of my passionate pursuit. Join me in making and decorating them! The entire process will probably take 3-4 hours but you are welcome to stay for however long. Also you'll get to eat some at the end!
\subsection{Make you any ice cream flavor}
Daniel Daugherty and Jeremy Garcia (Daniel.Daugherty.and.Jeremy.Garcia@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Dan and Jeremy will make you a tub of literally any ice cream flavor and you get to eat all of it
\subsection{Surprise Delivery of Homemade Macarons}
Emily Lepert (Emily.Lepert@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will deliver boxes of homemade French macarons to you sometime this year for a total number of macarons equivalent to the winning bid (ie: 20\$ -\textgreater  20 macarons, 31\$ -\textgreater  31 macarons, etc...)
\subsection{Dumpling Cafe}
Kevin Zhang, Jingyi Xu, Yuzhong Huang (Kevin.Zhang,.Jingyi.Xu,.Yuzhong.Huang@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
We'll make dumplings for you! For every dollar you bid, we'll make one dumpling, i.e. \$20 = 20 dumplings handmade and cooked for you (or preserved for later, your choice). Feel free to make bids individually, or as a group as large as you want! Dips and plates provided at the time of the meal, we'll meet later to discuss filling types and timing. Also, for every \$50, we'll also make an asian cuisine dish to go with your dumplings, i.e. \$100 = 100 dumplings + 2 asian dishes. Not convinced? Check out my instagram, kzhang8850, to see my cooking and what kind of delicious food we can make for you! (Note that my instagram is only for myself, with three of us we can make stuff even better than I could alone!)
\subsection{Gluten Free Brownies/Cookies}
Jessie Potter (jessie.potter@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will bake you something- everything I have to bake with is gluten free, so whatever I bake you will be too. It will probably be either like brownies or cookies.
\subsection{Homemade Reese's Peanut Butter Cup Chocolate Chip Cookies}
Stephanie Hill (Stephanie.Hill@olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Four dozen (48) homemade Reese's peanut butter cup chocolate chip cookies.  These are mini Reese's peanut butter cups surrounded by a chocolate chip cookie - a perfect combination of peanut butter and chocolate! You pick the day you want them.
\subsection{Sourdough starter pack}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I've been baking sourdough (also known as friendship bread, aw!) for the past year or so. I use a mother/starter that has been around since 1998 that was smuggled from Denmark to Australia to Canada (twice!). If the bidding goes over \$50, I'll figure out how to get part of the starter to you so that you too can share in that heritage. I've also started my own mother from spores in the air, and will talk you through that process as well.

I will send the winner my recipe, and we will become 'bread buddies', telling each other when and what we bake, and share pictures.
\subsection{Bread (surprise)}
Matt Ruehle (matthew.ruehle@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top 5 bids\newline
At some point this year - probably within the next couple of months - I will find you and give you a loaf of fresh bread. Let me know if you have any dietary restrictions!
\subsection{Creamed Honey with Strawberry}
Sharon Woodward (Sharon.Woodward@olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
 8oz. jar of creamed honey with strawberry
\subsection{Creamed honey with lemon}
Sharon Woodward (Sharon.Woodward@olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
8 oz. jar of creamed honey with lemon
\subsection{Creamed honey with blackberry}
Sharon Woodward (Sharon.Woodward@olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
8 oz. jar of creamed honey with blackberry
\subsection{Homemade Dessert}
Siena Okuno (siena.okuno@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top 2 bids\newline
Pick a delicious dessert and I'll make it! Some favorites: nutella stuffed donut holes, cookies (whatever kind you like), frozen bars, cookie dough, poptarts. We can work together to make sure I customize it to your needs/wants (and so I know I can make it in the first place).
\subsection{Kombucha Goodies}
Carly Ingrao (carly.ingrao12@gmail.com) \\
Starting Bid: \$2 \\
Winner(s): 
Top 2 bids\newline
In the past year, I've gotten into brewing my own kombucha. If you win this item, you'll get your very own bottle of fizzy, delicious, fruit-infused kombucha, a hunk of extremely-productive SCOBY so you can brew your own, a couple of glassware items that I personally use for brewing, and my recipe/tips and tricks! It would be best if you are from Boston or live in the Boston area.
\subsection{Sourdough Goodies}
Carly Ingrao (carly.ingrao12@gmail.com) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
I HAVE TOO MUCH SOURDOUGH STARTER. If you win this item you'll receive a little bit of what I've got and a loaf or two of fresh sourdough (or other type of bread of your choosing, made using the starter). This item is probably best for people local to the Boston area.
\subsection{Make a dessert inspired by you!}
Chloe Grubb (chloe.grubb@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
During a brief meeting, maybe over tea, I will try to learn more about you and your personality. I will then create a dessert that, to the best of my ability, is inspired by you as a person in all your glory.
\subsection{Five Guys }
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$3 \\
Winner(s): 
Top bidder\newline
We will go to five guys and I will buy you a burger, fries, and a Milkshake. You could do this yourself but its better with my company and doing it for charity. I will do my best to tell you random stories from my time at Olin during the meal.
\subsection{Chipotle Friday!}
Peter Seger (peter.seger@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Come join me (and usually a bunch of other people) on a Chiptole Friday run! I'll drive you there (and even back!) and pay for your burrito/tacos/bowl.
\subsection{Bread (non-surprise) }
Matt Ruehle  (matthew.ruehle@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Let me know a kind of bread and a day (at least a day in advance), and I'll try to make that bread for you and deliver it. Lamentably, I do not have a sourdough culture, but most other types of bread are fair game!
\subsection{Emergency Ramen}
Alexander Li (Alexander.Li@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I'll come make you ramen when you need it if I'm awake-- limited to 5 times.
\subsection{My dad will make baklava for you}
Alia Georges (alia.georges@olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
My dad is Lebanese. He's a cook. He will make you a large quantity of baklava.
\subsection{Amish Friendship Bread Starter}
Erika Swartz '12  (erika.swartz@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
My family has been making Amish Friendship Bread from the same starter since 2008. If you win this item, I will overnight a starter to the address of your choosing.
\subsection{IPA Heaven }
Keenan \& Scott (Keenanzucker@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Scott and Keenan are big ol beer snobs, and we will give you 4 pint-sized different IPAs curated from our hearts and souls. They will be absurdly hoppy, juicy, citrousy, and beer-y. 21+ pls
\subsection{Hangout with us}
2NW Suite (Robbie, Kai, JC, Anna, Sabrina, and Giulia) (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$6 \\
Winner(s): 
Top bidder\newline
We will open our suite up exclusively to you and a small group of friends (5ish?). We have plenty of sausages and pretzels leftover from Sausagefest so refreshments will be plentiful and delicious.
\subsection{I Can Fix You a Drink}
Sophia Nielsen (Sophia@students.olin.edu) \\
Starting Bid: \$7 \\
Winner(s): 
Top 5 bids\newline
ModSim or E+M or SCOPE got you down? Does politics make you sad? Afraid we're all going to die because of global warming? Well I can't fix that...but I can fix a drink! I will make you any Bourban cocktail of your choosing. You won't regret it. I make a mean Bourban Rickey.
\subsection{Make you Tacos al Pastor}
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
I will make you and 5 friends Tacos al Pastor. The meal may or may not be accompanied with some other Mexican refreshments.
\subsection{Cupcakes}
Jamie O'Brien (jamie.obrien@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
Choice of flavor cupcakes with  frosting
\subsection{Monthly box of vegan baked goods}
Alia Georges (alia.georges@olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
I will make and bring you fresh vegan baked goodies once a month for the rest of the school year. Like one of those subscription boxes but better/homemade. Will take into account flavors and ingredients you love/hate. May include pictures of my cat George.
\subsection{Andrew makes you some sushi}
Andrew Pan (andrew.pan@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Eat a few rolls of sushi made by Andrew/anpan/whatever.  If you want to learn how to make sushi, I can teach you the process too!
\subsection{Turn Water Into Wine}
CUAHSI SCOPE team (Andrew, Celina, Keenan, Mackenzie, Patrick) (celina.bekins@students...) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
We're the water SCOPE team. We like wine. You like wine. Come be awesome with us. Under 21, you just get water. (For a group of up to 5)
\subsection{Lunch at Raising Cane's}
Max Dietrich (maxcdietrich@students.olin.edu) \\
Starting Bid: \$15 \\
Winner(s): 
Top bidder\newline
Raising Cane's is a really good fried chicken restaurant.  Unfortunately there is only one in the whole state of Massachusetts, and it's in Boston.  If you win this item I will take you and a friend on a all expense paid trip to this restaurant.
\subsection{Some form of Sugar+Butter}
Lindsay Gordon (lindsaygor@gmail.com) \\
Starting Bid: \$15 \\
Winner(s): 
Top bidder\newline
I've taken a few professional baking courses over the past few years and would love to share my enthusiasm for baking with a lucky recipient. I can make shippable goods if needed or if you're in the Bay Area, I can make fancier pastry and Viennoiserie goods.
\subsection{Olin Maple Syrup}
Nick Tatar (nick.tatar@olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
8 Bottles of Olin Maple Syrup. Handcrafted and made from Maples trees on campus and the surrounding neighborhood.
\subsection{Harris Family Thanksgiving dinner \& more!}
Scott \& Jody Harris (scott.harris@olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 4 bids\newline
Are you stranded on campus this Thanksgiving? Is your mom a terrible cook? Here is a chance to have Thanksgiving dinner with us, our whacky friends and anyone else that drops by. Join us for some amazing food and fun activities. Ask anyone who has eaten at our house... Jody is a fantastic cook and nobody leaves hungry.

On Thanksgiving day, I will pick you up (if you do not have a car) and bring you to our house in Acton for a GIANT meal. You will be an honorary member of my  family for the day. In addition to stuffing our faces, in past years, we have done mad science (usually involving liquid nitrogen), hiking in the woods between courses, working in my shop, camp fire and snow-ball fights. Also... for the 5th year in a row, we will do M\&M bingo with FABULOUS prizes. 

I will drop you back at Olin in the evening.

For the top 4 bids.
\subsection{Baking at ERD's}
Emily Roper-Doten (emily.roper-doten@olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
Come do some baking at ERD's house in Medfield! Cookies? Pie? Cake? You pick! We'll make some tasty baked goods for you to bring back to campus. Group size: 4-6. Note: I have a dog, which could be a pro if you need some puppy therapy or a con if you're allergic.
\subsection{StAR Dessert Bar}
StAR (ashlee.talbot@olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 3 bids\newline
Do you enjoy tasty treats? Do you want to hang out with people from the best office on campus?  If so, the StAR staff is more than happy to help! You and 5 of your closest friends will have the opportunity to partake in delectable delights made by your very own StAR team! What type of delights you ask? Well, there's brownies, and cookies, and cupcakes, and cake, and fudge bars, and icecream, and these little blue-ball cake things that no one can really name but that are absolutely delicious! Top three bids win!
\subsection{Ice Cream A Lot}
Sunny Shroff, Cesar Santana (suraj.shroff@students.olin.edu, cesar.santana@students.olin.edu) \\
Starting Bid: \$25 \\
Winner(s): 
Top bidder\newline
We love ice cream, and you do too. Each month for the rest of the school year, we will take you out for, and buy you, ice cream. For each additional \$25 above the starting bid, you can add a friend to the item (maximum of 5 friends).
\section{Events}
\subsection{Singing performance}
Junwon Lee (junwon.lee@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 5 bids\newline
I will perform my 5 favorite songs that will cheer you up.
\subsection{Jet-Skiing or Lake Washington Boat Tour (in Seattle area)}
Kelly Brennan (kelly.brennan@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will be give you a jet ski adventure or take you on a Lake Washington boat tour! Your choice. 

For the jet ski adventure: (limited to 2 people)
- If bidding goes above \$20, I'll let you drive. 
- If bidding goes above \$50, I'll let you drive by your self.

For the Lake Washington Boat Tour, there are a couple options: (limited to group of 8 or less people)
- We can do a loop around Mercer Island and up to Bill Gate's house. 
- We can go wake-boarding and/or water skiing. 
Note: If bidding goes above \$50, drinks (beer, wine, soda, etc.) and appetizers included. If bidding goes above \$100, we can do dinner at my house on the lake.

*This SERV auction item does not expire. We can do it any time that you and I are both in the Seattle area in the spring, summer, or early fall.
\subsection{Y Tu Mamá También}
Mackenzie Frackleton and Linnea Laux (linnea.laux@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Watch the legendary 2001 Mexican film "Y Tu Mamá También" with the guidance and support of Linnea and Macklefrackle. Mack did an OSS in Mexican Film, and Linnea has had other relevant Mexican experiences, so you will be in qualified and caring company.  The higher the bidding goes, the more authentic we will make the experience. If bidding reaches \$5000, we will take you to Mexico and reenact the road trip in the film.
Fair warning: the film is sexually explicit, and this experience will make more sense to you if you understand Spanish.
\subsection{Ron's Snacks Easter Egg}
Joe Sutker (Joe@students) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
Do you have a favorite food that you want to star in AVPM? Do you want to watch me eat something weird? Do you like forcing people to do your bidding in a really subtle way? Then this is the item for you.

I'm playing Ron Weasley in the upcoming FWOP performance, and I will be eating various snacks on stage. For the measly price of whatever you end up winning with, you get to pick a snack for me to eat during the show. The top three bidders each get to choose a snack (one for each night) that I will eat. I will try to finish your snack of choice before leaving the stage. Your choice will be subject to director approval, but keep in mind that I will eat most things.

Rules:
- cannot be alive (can have been alive at one point)
- must be at least technically edible
- nothing illegal
- nothing that will put me or my fellow cast members in danger (specifically peanuts are not allowed, no matter how delicious)
- I must be able to hold it reasonably
- must be reasonably priced (no caviar)
\subsection{Take you to brunch/lunch/dinner/dessert in Cambridge!}
Lauren Gulland (Lauren.Gulland@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I've found some awesome places to get your foodie fix on so far this semester -- let me take you to them! We can optimize for price, genre of food, portion size, fanciness, you name it. Come party with me in Cambridge, and get some free food while you're at it! 
If this happens to go over \$15 or something I'll split your lyft/uber costs if you want to get a lyft into the city, just to further incentivize you to pop the Olin bubble. :) You can bid with multiple people (the more the merrier!) but also \#collegebudget so maybe don't bid with all of Olin's population?
\subsection{Revitalize, Rejuvenate, Recharge }
Nina Tchirkova and Elena Meyerson (Nina.Tchirkova.and.Elena.Meyerson@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
Let us treat you to a restoring yoga sesh and then a quick trip to Wellesley to get smoothie bowls at Cocobeet! 
No yoga or smoothie bowl experience necessary, if the bidding is \$20 or more you can bring a friend! If desired, a well lit insta-worthy pic will be provided as well. 
"My philosophy is that if it isn't fun you won't do it" - Sara Ivanhoe
\subsection{Kitteh Time w/ Ava}
Brandon Chiou, Carly Ingrao (brandon.chiou@alumni.olin.edu) \\
Starting Bid: \$2.27 \\
Winner(s): 
Top bidder\newline
Ava is our sassy, two year-old black cat. Her favorite toys are crumpled receipts and human appendages, and she's addicted to olive oil / butter / saturated fats.

Top bidder of this item will receive kitteh time with Ava at our Cambridge apartment. Max group of two, and receipts and fats will be provided. Bring your own appendages.

For some ridiculous anthropomorphized narration and silly cat puns - Ava's IG: @ava.the.asshat
\subsection{Parcel B Secrets Tour}
Ben Ziemann (Benjamin.ziemann@students.olin.edu) \\
Starting Bid: \$3 \\
Winner(s): 
Top bidder\newline
Parcel B is a magical place and strewn throughout it are some incredible secrets that I'd love to show! Bring a friend and take a walk with me to some of the most interesting, weird, and my favorite places around Parcel B! 

Be prepared to walk and climb through the woods.

Depending on how high this gets I will take more people.
\subsection{Movie Night with Sophie and Siena}
Siena Okuno and Sophie Schaffer (Siena.Okuno.and.Sophie.Schaffer@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Do your friends hate your movie choices? Do you lack a projector? Then hang out with us! Pick any movie and we will be so excited to watch it with you and up to 6 of your cool friends. We'll provide the snacks, baked goods, and beverages. You provide the company and amazing movie recommendations.
\subsection{Midnight adventure}
Utsav Gupta (utsav.gupta@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 4 bids\newline
Go on a hiking adventure to the Needham Town Forest and see the famed Martini Junction at midnight
\subsection{An SF Adventure}
Shane Skikne (ShaneSkikne@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Live in SF? Visiting SF? This item entitles you to one truly memorable San Francisco Adventure. You'll send me a list of your passions and interests and I'll ignore that and take you to my favorite SF spots. 
If bidding goes above \$10, we're getting donuts.
If bidding goes above \$100, we're adding a homemade cheese tour of Marin. 
If you want, we can do this tour on mopeds.
\subsection{Watch first snow from our window seat}
frankie Devanbu, Gaby Clarke, Izzy harrison, Walker Trelease, mikhaela dietch, brennan vandenhoek (frankie.Devanbu,.Gaby.Clarke,.Izzy.harrison,.Walker.Trelease,.mikhaela.dietch,.brennan.vandenhoek@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
we live in 2 east hand have great views of parcel b. come hang out in our cozy window seat. we will make you hot chocolate. you can bring a friend
\subsection{Bedtime Storytime with Ashlee}
Ashlee Talbot (ashlee.talbot@olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Have you ever crawled into bed at night, and just wished you had a snack and maybe a story or two? Ashlee is here to help you out! On a night of your choosing, she will arrive at your room or suite with a tray full of cookies, a glass of milk, and a storybook of your choosing. Voices and goofy pajamas guaranteed.
\subsection{VIP Otamatone Concert tickets}
Jonathan Zerez; Mark Goldwater (Jonathan.zerez@students.olin.edu; mark.goldwater@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 3 bids\newline
You get good seats, neat snacks, and the ability to choose a song that we play.
\subsection{Date Night with Mack n' Nina}
Mackenzie and Nina (mack@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
Experience a dream Date with Mackenzie and Nina. Our night out in Boston's Historic North End with its glorius Improvisational Comedy scene, made even sweeter by canolis in the North End itself  The night will include a show at Improv Asylum with dessert before or after. If bidding rises about \$30, dinner in the north end will be included, and the reservation will gain prestige as overall item price rises. If item price rises about \$75, you can bring a friend to share the wonder of the best date of your life, and if price rises above \$200, you'll get the delux package (think: brunch)

https://drive.google.com/file/d/0B7EWpy3rlpIjZ0M5OU9XSDdRNDA/view?usp=sharing
\subsection{Sushi with Alex B and Anna}
Alex Bahner and Anna Griffin (alexander.bahner@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Dinner with Alex and Anna, 2 maki madness rolls and another person of your choice
\subsection{Movies with Krys \& Pete}
Emily "Pete" Petersell \& Krystal "Krys" Burgos (emily.petersell@olin.edu; krystal.burgos@olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Krys \& Pete will take you and up to three friends (maximum group of four) to a movie of your choice! You pick the date and the film, and we'll drive you to the theater, pay for tickets and snacks, and drive you back to Olin afterward!
\subsection{W(h)ine and Cheese}
Shruti Iyer, Maggie Jakus, Brenna Manning, Mary Martin (shruti.iyer@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
We love complaining! We know that you love complaining! Let's get together. We'll bring cheese and grape juice. Open to groups of 2-3 people.
\subsection{FWOP Tickets for Life}
Mitch Cieminski (mitchell.cieminski@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
I am the proud holder of FWOP Tickets for Life (courtesy of Philip Z. Loh, who buys my ticket for every FWOP show I attend), and I'm going to share the love!

So, same conditions as I got. For as long as: (1) You live, (2) I live, and (3) FWOP (or another Olin-based theater organization) is around, I will buy your FWOP tickets (limit 1 per production) so all you have to do is simply attend and enjoy the amazing feeling of royalty. 

Winners above \$25 will get the definition of FWOP expanded to "Any Olin performance art show on-campus that costs money." 
Winners above \$50 will instead get TWO tickets per production, and some money for snacks.

The top two bidders will each win this item.
\subsection{Movie night in our suite}
frankie Devanbu, Gaby Clarke, Izzy harrison, Walker Trelease, mikhaela dietch, brennan vandenhoek (frankie.Devanbu,.Gaby.Clarke,.Izzy.harrison,.Walker.Trelease,.mikhaela.dietch,.brennan.vandenhoek@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
We have a dope projector in our dope suite with a 120" (10 foot) screen. come watch a movie with us, you can choose it (but we get veto power) and we will make you popcorn. if it goes past \$10 you can bring a friend, and one more friend for each additional \$5
\subsection{Taco Tuesday with your local San Diegan*}
Gaby Clarke (gaby@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
We'll go get tacos at one of the best taco spots in Boston. Horchata (or other beverages) included. *Need not be redeemed on a Tuesday
\subsection{W(h)ine}
Mackenzie Frackleton, Ian Paul, Jeff Pflueger, Cesar Santana, Cecilia Diehl, Andrew Deaver (mack@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Come W(h)ine with us. Wanna boda box and betch? (under 21 you can still whine and get a tasty, age appropriate drink) you can even bring up to five friends!
\subsection{Taco Quest}
Ian "no last names" Paul, Evan Newsch, Sam4CORe (pizza@students.olin.edu) \\
Starting Bid: \$15 \\
Winner(s): 
Top 2 bids\newline
Includes one Taco Bell meal of your choice, one laser tag game (additional laser tag is possible), and a two-way car ride in the MemeMobile with excellent* music. If bidding goes over \$100, we will take you on an all-day immersive QuadBell™ experience, including all four meals (midnight is a meal) at Taco Bell, laser tag in the evening, and maybe a viewing of some subset of the Star Wars prequels.
\subsection{Theater or opera outing (SF Bay Area)}
Ilana Walder-Biesanz (izwb.calico@gmail.com) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
I work as a theater and opera critic. This means I can get a pair of free opening night tickets to nearly any show in the Bay Area. (Really -- they even gave me free Hamilton tickets!) Pick a play, musical, or opera you really want to see (give me advance warning), and come with me as my +1! If bidding goes above \$60, I'll buy you a nice dinner beforehand, too.
\subsection{Consecutive Days of OPIUM Shows}
OPIUM (william.wong@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
For every \$20 donated, OPIUM will perform one 15-minute show on a consecutive day.  Ex. \$100 = 5 straight days of shows

Extras:
\textgreater \$100: Each show will have a randomly-chosen theme (ex. Singing, One-Line-Per-Scene, Boner Game, Calvinball).  We won't know the theme until the show starts.
\textgreater \$200: In one show, we will pretend to be a club we're not qualified to be (Powerchords, ORO, OCO)
\textgreater \$250: You get to choose the theme for one show.
\textgreater \$300: Every fifth show we will use a random number generator to decide the location of the show.
\textgreater \$400: We will do one late-late show sometime between 1am - 8am
\subsection{Indoor climbing}
Avery Louie ('14) Nick Lapin ('15) (inactive.e@gmail.com) \\
Starting Bid: \$25 \\
Winner(s): 
Top bidder\newline
Nick and I will take you climbing at CRG Watertown!  We can provide entry for two people.  We can pick you up from Olin (or somewhere nearby) and drop you off there as well.

If you are totally new, we can "show you the ropes".
\subsection{Your North Friday}
Rowan, Onur, Henry, Adam, Annie, Matt, Toby, et al. (rowan.sharman@students.olin.edu) \\
Starting Bid: \$32 \\
Winner(s): 
Top bidder\newline
A catered movie night exclusively for you and your friends in your favorite chill inclusive hangout space. Featuring: catering by The Space Bar and Coffee Space, cookies by Annie, popcorn by Matt, and your choice of content on a 9' 1080p screen with 5.1 surround sound.
(The loft has been experimentally tested for up to 20 people, but we estimate the failure capacity to be around 60. It's pretty crowded by the time you get to 10 people though.)
\subsection{taste / talk about wine}
Brandon Chiou (brandon.chiou@alumni.olin.edu) \\
Starting Bid: \$40 \\
Winner(s): 
Top bidder\newline
Great wine doesn't have to be expensive (\textgreater \$25). We'll taste four biodynamic wines tailored to your preferences and talk about them and *how to taste* - all without the pretension found in wine culture. If bid reaches \$75, I'll pair some finger foods.

Some of my favorite producers in case my taste is called into question: Jo Landron, Kate Norris, Broc, Vietti. I also work at a small, biodynamic-focused wine shop in Central Square.

Max group of 5, and event limited to Cambridge / Greater Boston area.
\subsection{beer + perks}
Brandon Chiou (brandon@centralbottle.com) \\
Starting Bid: \$40 \\
Winner(s): 
Top bidder\newline
True millennials have side hustles, and mine is as a beer buyer for Central Bottle - that is, I taste through samples and select the beer to be sold there.

Winning bidder will provide me their taste preferences and I'll put together a flight of four beers per. Bid goals:

- \$75, + cheese pairings for each
- \$100, + my in-store discount (one item pp) + above
- \$150, + wholesale discount (one case pp) with the distributors I work with (hundreds of domestic and foreign microbrews) + above

Max group of 4. Limited to Cambridge / Greater Boston area. 21+ only.
\subsection{Adventure with Walker and Brennan}
Walker and Brennan (walker@students.olin.edu) \\
Starting Bid: \$50 \\
Winner(s): 
Top bidder\newline
We will take you and a friend on an adventure. You name the when, we name the what and the how. We are avid adventurers and have a tendency to get in slightly over our heads. All technical equipment will be provided, if winning bid passes \$150 we will make it an overnight.
\subsection{A Hike in the White Mountains!}
Avery Louie (ME, '14) , Nick Lapin (ME, '15) (inactive.e@gmail.com) \\
Starting Bid: \$50 \\
Winner(s): 
Top bidder\newline
Nick and I will take you on a trip to the Whites to go hiking!  We can take you+another person somewhere easy, or somewhere challenging!  Date to be scheduled before the end of this school year by mutual agreement.  Climbing is also a possibility, if you are into that.

We will do our best to help you get any gear you need together, but it is up to you to supply basics like clothing for yourself.

We can take 2 people, or 3 if you really want to squeeze.
\subsection{Brunch and Shopping with the Deans}
Emily Roper-Doten and Jessica Townsend (emily.roper-doten@olin.edu) \\
Starting Bid: \$100 \\
Winner(s): 
Top 5 bids\newline
Need fashion advice? Want to spend a little QT with ERD and JT? Join Emily and Jessica for brunch followed by an afternoon of shopping! (For one group of about 5)
\section{Lessons}
\subsection{Pun01}
Nicholas Sherman (Nicholas.Sherman@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top 2 bids\newline
Have you wanted to learn the secret of punmaking? Well, you're in luck, as winning this will grant you an exclusive 1 hour lesson in punning from me!
\subsection{Learn a Cartwheel Guaranteed}
Eamon O'Brien (eamon@piratecat.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top 5 bids\newline
I will teach you a cartwheel. I promise it will work if you have at least three limbs. If you're good at cartwheels you can learn other stuff like handstands and handsprings.
\subsection{Convos with Communists}
erika serna (erika.serna@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
I am so up to talk about communism and provide hot chips.
\subsection{Olinsight from Graham}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I arrived at Olin in 2009, took a year-long LOA, worked in the admission office, and joined the Alumni council. I've rubbed elbows with more than a few historical figures in this place, and will gladly share what I know with the right person... for the right price.
\subsection{Burning Man Recommendations}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I've been to Burning Man three times and love to talk about it. If you're interested in going or learning more, get at me! I can tell you what you need to know, or what you didn't know you needed to know.
\subsection{soul cycle with sabrina }
Sabrina Tamames (sabrina.tamames@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 2 bids\newline
come join me on a super fun and hard work out class at soul cycle! **must be 18+**
\subsection{Boxing lesson with the coolest }
Anika Payano and Sabrina Tamames (sabrina.tamames@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
come join us at a class at The Ring Boxing Club!!
\subsection{Water Balloon Lessons}
Aaron Greiner, Keenan Zucker, Patrick Huston (aaron.greiner@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
That's all you get to know.
\subsection{Learn to ride a boosted board}
Brennan VandenHoek  (Brennan@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 3 bids\newline
Want to be cool like Casey Neistat? I will teach you how to ride a boosted board and let you take my board out for a spin.
\subsection{Lesson on an Art of Choice}
Emma Pan (emma.pan@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
An hour long lesson on drawing, singing, violin, or viola. For drawing I can give tips on sketching, photo-realism, different techniques, and multi-mediums. I've been learning these things for more than 12 years.
\subsection{Bike Maintenance lesson}
Shawn Albertson (shawn.albertson@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
Have a bike that needs fixing? Want to learn about fixing bikes? I have some experience with bicycle maintenance and would love to pass this knowledge on to you. Come with or without experience, but be ready to get your hands dirty!
\subsection{Interview practice}
Ilana Walder-Biesanz (izwb.calico@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
I've been through a lot of interviews: job interviews, grad school admission interviews, fellowship interviews, practice interview for those interviews, etc. I've also conducted interviews, both for hiring product managers and for potential Olin students. Let me conduct a practice interview with you via a phone call or Skype! I suggest you use this to prepare for product/program manager or graduate fellowship interviews, since those are what I know best.
\subsection{Stitch 'N Bitch (aka learn to knit/crochet!)}
Alia Georges and Krystal Burgos (alia.georges@olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
The fiber arts fanatics of the Office of Admission \& Financial Aid (Alia knits; Krystal crochets) will provide a customized knitting and/or crochet experience for a group of up to 4 people. We will help you find a pattern for something you want to make, provide the supplies, and teach you how to do it!
\subsection{Teach you to drive stick}
Walker Trelesae (Walker.Trelesae@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
My car has a stick shift. It fun. Now you too can have fun.
\subsection{Twerk Lessons}
frankie Devanbu, Gaby Clarke, Izzy harrison, Walker Trelease, mikhaela dietch, brennan vandenhoek (frankie.Devanbu,.Gaby.Clarke,.Izzy.harrison,.Walker.Trelease,.mikhaela.dietch,.brennan.vandenhoek@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
our suite will learn how to twerk with you. frankie and youtube will be the teacher
\subsection{Teach you how to drive stick}
Gaby Clarke (gabrielle.clarke@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
I'll give you a lesson on driving manual, probably better than Walker can. We'll test drive in my Mini Cooper (excellent for bank heists). (Walker would like to point out that his car is faster)
\subsection{Teach how to change your oil}
Brennan  (Brennan@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
I will teach you how to chang you oil (it is a lot easier then you might think). If the bid goes over \$50 I will also teach you how to change your brakes. I will provide the tools but not the oil or other parts
\subsection{Learn How to Be a Disc Golf Chumpion}
Max Dietrich, Steven Meyer (max.dietrich@students.olin.edu, steven.meyer@studetns.olin.edu) \\
Starting Bid: \$15 \\
Winner(s): 
Top bidder\newline
Legacy and Gunslinger will give you personal lessons on how to play disc golf like a chump.  We guarantee* that you will be able to achieve at least a 650 player rating.  At \$30 we will take you to play at the world famous course at Maple Hill
\subsection{Mixology}
Taylor Sheneman (taylor@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 3 bids\newline
I will haphazardly teach you about the basics of mixology, and get you started down the rabbit hole of craft cocktails. Learn about balance, ingredient selection, cocktail history, spirits, measurement techniques, ice, presentation and more from someone who's spent a slightly obsessive amount of time doing all this. (Minimum bid includes the cost of the equipment you will walk away with)
\subsection{Ride and Drive a 2012 Corvette Grand Sport}
Kevin Comellas (Kevin.Comellas@Olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
Learn what it is like to ride and drive in a car that is completely and totally irrational for New England! Chef Kevin will take you for a spin and show the ins and outs of America's Sport Car (except if you live in Massachusetts where it makes no sense, why did I buy this???) Then, he will let you drive through scenic Needham and Rt.9 (weather permitting, or it will have to wait until spring).
\subsection{Music Lesson!}
Flynn (flynn.michhael-legg@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 2 bids\newline
I'll teach you a song or some basic theory or whatever you wanna know! I play piano, guitar, drums, bass, saxophone and more. Can play whichever you want!
\subsection{Teach you to drive stick}
Ariana Olson (Ariana.Olson@olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
Learn how to drive a manual! I will teach you the basics of driving a stick shift in my car. Each lesson would be an hour block of time, and the number of lessons depends on how high the bid goes. You must already have a license to receive lessons.
\subsection{I will teach you card magic}
Braden Oh (Braden.Oh@students.olin.edu) \\
Starting Bid: \$25 \\
Winner(s): 
Top 2 bids\newline
I used to work professionally in Hollywood doing card magic. I'll give you a reasonable number of hours of lessons and teach you some great party tricks!
\section{Arts and Crafts}
\subsection{Really Rad Detailed Vinyl Sticker}
Katie Thai-Tang (katherine.thai-tang@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
I'm pretty good at making giant super detailed stickers from photographs etc. I can totally make you one of whatever you want and put it up for you without any bubbles *thumbs up*
\subsection{String Art Embroidery Piece}
Coleman Ellis (coleman.ellis@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I'll make you a custom string art embroidery piece on paper (custom meaning of a design and colors of your choosing). See https://imgur.com/a/vnxJG for examples .And seriously, look at the examples. They're really cool and really hard to describe with words. If the bid gets above \$25, I'll frame it!
\subsection{A Chrochet Kraken}
Paige Pfenninger (Paige.Pfenninger@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
1 small crocheted kraken. The design was featured in the POE project last year. (Pictures can be found at http://poe.olin.edu/2016/clocks/)
\subsection{Sketch}
Lydia Zuehsow (Lydia.Zuehsow@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
Terrible at art?
I will draw you ink lineart of any one thing of your choice.
(no NSFW images)

The complexity of this image will scale with the amount bid.
You determine the style.

Get a picture of your product, original character, or even yourself.
\subsection{Digital Caricature}
Jeremy Ryan (jeremy.ryan@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Given a photo, I'll draw a digital cartoon of you or a person of your choice.
\subsection{Crochet Pride or Striped Hat}
Hannah Kolano (Hannah.Kolano@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will crochet you a striped hat, you choose the colors. Especially happy to make a pride flag into a hat.
\subsection{a weird cartoon OR I'll decorate a thing}
Hadleigh Nunes (hadleigh.nunes@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 3 bids\newline
Pick one: I will draw you a weird drawing or cryptic prophesy diagram. OR I will decorate something. like a phone case. Or a binder. Or a calculator. A shirt. Shoes. A multi- tool.
\subsection{Coloring with Adva}
Adva Waranyuwat (adva.waranyuwat@olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top 5 bids\newline
Adva will have some coloring postcards and markers and we will spend 1-2 hours coloring together!  Up to five students can join me!
\subsection{Crochet Star Wars Figure}
Hannah Kolano (Hannah.Kolano@students.olin.edu) \\
Starting Bid: \$2.5 \\
Winner(s): 
Top bidder\newline
I will crochet you a ~4" Star Wars character of your choice. If the bid reaches \$40 I will even try a non-human.
\subsection{Screenprinted Olin Swag}
Alex Chapman (alex.chapman@students.olin.edu) \\
Starting Bid: \$4.2 \\
Winner(s): 
Top bidder\newline
I will design and print an olin (or non-olin) related design onto the clothing type of your choice.
\subsection{Tunes 4 U}
David Freeman \& Niyi Owalabi (david.freeman@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
we'll make u a personalized mixtape (based off discussion \& inquiry), hang out with u in our speakered-out room, or do a little dance party. This is up to you, we're just a music-lovin crew!
\subsection{Plasma Cut You a Thing}
Claire (clairekincaid98@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I'm pretty good at plasma cutting (CNC and hand) and I will plasma cut you a thing of your choice and design.  Grandioseness of cut thing is linearly scaled by the amount of money you have bid (aka if you win this for 5 bucks I'm not going to cut you a huge art triptych)
\subsection{Write a Quote in Calligraphy}
Brandon Zhang (Brandon.Zhang@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 3 bids\newline
Will write up to 50 words in Italic script, can use dark blue, black, or gold ink
\subsection{Origami Flower Fairy Lights}
Sophie Schaffer (sophie.schaffer@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Custom origami fairy lights, tell me your favorite colors and I will make you paper fairy lights that shine those colors!
\subsection{Ceramics}
Mark Somerville (mark.somerville@olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 5 bids\newline
Mark likes to play with clay.  He would love to make something just for you.  A mug?  A cereal bowl?  A vase?  A large serving bowl?  A tea set?  The possibilities, while not endless, are vast -- if the price is right.

Any bid over \$20 will get a mug or a bowl.  Bids over \$50 can make custom requests, subject to negotiation.
\subsection{Make Something For You in the Shop}
Sunny Shroff (suraj.shroff@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I will make something of your design for you out of metal, wood or another machinable material. If the bid goes above \$25, I will design it for you too.
\subsection{Choose my hair color}
Andrew Pan (andrew.pan@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Winner gets to choose my (anpan, andrew pan, pandrew, *insert name here*) hair color!  If the bid goes above \$30, Max Wei will do his too
\subsection{2 pieces of Pottery}
Izzy Harrison (izzy@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
I make a lot of pottery and most of it is pretty mediocre. Ill let you have 2 things of your choice of my pottery stash. second highest bidder gets 1 thing.
\subsection{Vector Art Commission}
Mika Notermann (mika.notermann@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top 2 bids\newline
One vector art commission of reasonable complexity (I'm negotiable, but I'm by no means an expert at drawing things). As I aim to be vinyl-cutter friendly with whatever I draw, the art will likely be one or two-colored, though, again, this is negotiable. Basically, tell me what you want me to draw, and I'll do whatever is in my abilities to get it to you as fast as possible! I will send you an SVG file as well as the original Illustrator document, as well as the original sketch, if you want it.
\subsection{Handmade Glass Earrings}
Jayce (jayce.chow@students.olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Handmade dangling (not stud) earrings, either with a bead of your color choice or flowers.
\subsection{Mixed Blues Necklace}
Ruth Hunter (ruthphunter@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
34" single-strand of glass beads in a blend of blues with small golden accents. Blues tend towards moody "denim" shades, not bright blues.  Can be worn as a necklace (1 wraps) or bracelet (3-4 wraps).
\subsection{Red Glass Flower Pendant Necklace}
Ruth Hunter (ruthphunter@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
A heart-shaped glass pendant encapsulates a red flower on a copper-flecked black background.  Pendant is hung on an 18" necklace of red beads with cream, black, and copper accents, finished with a gold toggle clasp.
\subsection{Ambigram necklace}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top 3 bids\newline
One-of-a-kind personalized wrapped wire necklace that reads a word of your choice* both forwards and flipped backwards. Under \$50 = under 8 letters. Bid \$100+ and we can make it read one word one way and a different word of a similar length the other way. Shipping included to anywhere in the US or Canada.
*within reason
\subsection{Handcrafted cards with my photography}
Lindsay Gordon (lindsaygor@gmail.com) \\
Starting Bid: \$15 \\
Winner(s): 
Top bidder\newline
I love photography and enjoy printing out my photos, making them into cards and giving them to friends and family as gifts. You get to choose ten of my photos, I'll print them out and mount them on cards for you and you can treat your friends and family to some handmade snail mail. Check out some example photos at lindsaygordon.com/photography
\subsection{Nude with Fruit Calendar}
Emily Kohler, Andrew Pan, David Papp, Jonah Spear, Ariana Olson, Kim Winter, Ruby Spring (andrew.pan@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 3 bids\newline
We humble art enthusiasts have deigned to create a work of our own.  We are auctioning off an exquisite suite of photos depicting fine fruits paired with fine physiques, and nothing else (except for some calendar dates I guess).  Top 3 bidders will receive a calendar
\subsection{make you a jewelries}
Claire (clairekincaid98@gmail.com) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
I like to think that I'm real good a making jewelry, so I'll make you one if you win.  for minimum bid (20\$) you can get a handwoven copper bracelet.  For bids of \$50 or more you can have a small piece made of sterling silver and beach glass.  For a bid of \$75 or more, you can have a piece made of sterling silver with semiprecious stones.  If you donate more than \$100, come talk to me and we'll figure something out that's suitably grandiose.
\subsection{Chainmail Bikini}
Eric Jacobsen (eric.jacobsen@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
I will handmake a custom chainmail bikini.
\subsection{Small Welded Art Piece}
Siena Okuno (Siena.Okuno@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
I'll make you a (smaller than 24") welded structure / art piece. It could be a small sculpture out of nuts and bolts or a nice wine holder... or something else you would like. We can work together to make sure you get the most satisfaction out of your money.
\subsection{Custom Digital (or Traditional) Artwork}
Hwei-Shin Harriman (hwei-shin.harriman@students.olin.edu) \\
Starting Bid: \$25 \\
Winner(s): 
Top bidder\newline
One illustration of an object, character, landscape, photo, etc. of your choosing. The artwork will be painted digitally and can be printed up to the size of a medium-sized poster. Full color and any drawing/painting style is available. Samples are available at hweishin.carbonmade.com
\subsection{Make you a 30 second video}
The OG Sam \&\& French Matt (pizza@students.olin.edu) \\
Starting Bid: \$25 \\
Winner(s): 
Top bidder\newline
THIS SUMMER...*

TWO MEN.
THIRTY SECONDS.
ONE VIDEO.
YOUR IDEA.

From the award-winning** filmmakers who brought you instant classics such as DRIFTO and WILD WILD WEST HALL, comes the next summer* blockbuster. Except this time YOU'RE in the director's chair. Are you ready to be a part of Olin history?†



* fall
** last year's 30 second video competition
† we're going to cap this at 6 hours so it doesn't consume our lives, so set your expectations accordingly:)
\subsection{Teach You To Cut Rocks}
Claire Kincaid (clairekincaid98@gmail.com) \\
Starting Bid: \$50 \\
Winner(s): 
Top bidder\newline
I cut rocks into prettier versions of themselves.  I will teach you to do this, and you get to keep the rock you cut.  I am also perfectly happy to discuss crystals with you endlessly during this process.
\section{Miscellaneous}
\subsection{My Roommate, Kerry}
Missoury Lytle (missoury@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
Must go. Good for coffee shop and gym trips. Responds to Karen and Kansas.
\subsection{A Crisp High Five}
Sophie Schaffer and Siena Okuno (Sophie.Schaffer.and.Siena.Okuno@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
Not a flaccid high five. A CRISP high five.
\subsection{Dye my Hair!}
Nicholas Sherman (Nicholas.Sherman@students.olin.edu) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
You know what I haven't done in a while? Look ridiculous. So, come help me by choosing the color my hair will be! If you want, feel free to help dye my hair as well!
\subsection{Literally Nothing}
Joe Sutker (Joe@students) \\
Starting Bid: \$0.01 \\
Winner(s): 
Top bidder\newline
This is literally nothing. You get nothing from this except for the joy of donating money. Or sadness at the loss of your money. But it's a good cause.
\subsection{Marshadow Code}
Nathan (nathan.estill@students.olin.edu) \\
Starting Bid: \$0.25 \\
Winner(s): 
Top bidder\newline
A code for the Marshadow Pokemon in Pokemon Sun and Moon
\subsection{Add you on Facebook}
Serena Chen (serena.chen@students.olin.edu) \\
Starting Bid: \$0.5 \\
Winner(s): 
Top 2147483647 bids\newline
My legal name is Serena Chen, and my Facebook name is Bert Rito Chin. This SERV auction, you have the unique opportunity to buy my Facebook friendship. There will be different perks, kickstarter style:

For \$0.50, I will find your profile and add you on Facebook. Unlimited backers.
For \$5.00, I will do the above and also poke you (no guarantee of ever poking you again afterwards). Unlimited backers.
For \$50.00, I will do the above, and for the next year, I will react appropriately to all your posts and probably write nice comments on your profile picture. Max 5 backers.
For \$500.00, I will do the above, and you get the opportunity to change my Facebook name*. Max 1 backer.

* Cannot be offensive or my real name. It must also be something that Facebook will allow as my name.
\subsection{A Crisp Highfive}
Alexander Li (Alexander.Li@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
The first time I pass by you in the day, I will make sure you get a crisp high five. May take multiple attempts, but one of them will most definitely be crisp.
\subsection{Steven Meyer}
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Steven is my sib and as an older sib I want to make sure someone can take care of him when I'm gone. He likes cars and belly rubs. Highest bidder gets to keep him as of Jan. 2018. Groups are allowed.
\subsection{Dip Dye My Hair!}
Anne Ku (Anne.Ku@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I've never dyed my hair and I'm willing to try! For a minimum of \$1.00, you can choose what color (or dye, style, hair cut, etc. if you want full freedom) my hair will be. You can even help out with the dyeing if you want to!
\subsection{A Firm Handshake}
Justin Kunimune (Justin.Kunimune@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will shake your hand in a firm manner once.
\subsection{SHRED IT!}
Keenan  (keenan.zucker@students.olin.edu) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
SSSHHHHRRRREEEDDDD ITTTTTT!
\subsection{Pen pal for life}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
Buy this item, and I’ll write you a letter. Write me back, and I’ll reply, every time, for the rest of your/my life.
\subsection{Philosophy buddy for a month}
Graham Hooton (grahamhooton@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I like to learn what others think about some of the big questions in this world, and I’ve noticed that I think best by linking ideas, and communicating them to others. Let’s connect, grow, and support one another’s growth by sharing our deep and meaningful thoughts, observations, plans, and feelings by whatever communication platform fits best. Last year’s winner and I filled each other’s Facebook messenger inboxes.
\subsection{The Perfect Calvin for the Occasion}
Eric Schneider (franz.eric.schneider@gmail.com) \\
Starting Bid: \$1 \\
Winner(s): 
Top bidder\newline
I will do my best to collect Calvin and Hobbes strips for you that match a given theme/prompt. You can then use them however you want - to put on the wall, make into cards, give to friends, just keep around, whatever. Interpret theme as broadly as you want. Examples might be 'swimming', 'sleeping', 'Spiff', 'your favorites', 'teamwork', 'joy', 'bad food at dinner'.

I'll be using some combination of memory, books, and the links below to find comics, you're welcome to explore the links if you haven't seen them before!

To search for specific comics: http://michaelyingling.com/random/calvin\_and\_hobbes/
For comics: http://www.gocomics.com/calvinandhobbes/1985/11/18
\subsection{Speak Spanish with you}
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
I will speak Spanish with you and teach you Mexican slang
\subsection{European Postcards}
Meghan Tighe (Meghan.Tighe@students.olin.edu) \\
Starting Bid: \$2 \\
Winner(s): 
Top bidder\newline
I'm abroad in London this semester! The winner of this item will receive a postcard from each country that I visit! (Total expected to be 5)

I will mail the postcards domestically when I'm back in the States/put them in your Olin mailbox!
\subsection{Story TIme with Luis}
Luis F. Zuniga (luis.zuniga@students.olin.edu) \\
Starting Bid: \$4 \\
Winner(s): 
Top 4 bids\newline
I have a past rich with stories about chickens, axes, and windowless rooms.
\subsection{Crush a Cold One with Jonah and David}
Jonah Spear and David Papp (jonah.spear@students.olin.edu) \\
Starting Bid: \$4.2 \\
Winner(s): 
Top 2 bids\newline
Mystery
\subsection{Put a sticker on the 2018 Baja Car}
Juan Carlos del Rio (juancarlos.delrio@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Our car features the names of all of our sponsors and donors every year. You will get to put a vinyl cut sticker of your choice (pending captain approval) to join this illustrious group of Baja patrons. Your sticker will most likely be placed in the back of the firewall so everyone we pass (or passes us) can see it as we go by.
\subsection{Bitch and Brew}
Lauren Pudvan and Nicole Schubert (Lauren.Pudvan.and.Nicole.Schubert@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
We will drive you and up to two friends to Starbucks during rush hour and buy you each a drink. There will be copious amounts of road rage. Parental discretion is advised.
We ask for a donation of at least \$5 per person.
\subsection{Chattanooga Care Package}
Meryl Stark (meryl.stark@alumni.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Did you know Moon Pies are from Chattanooga? Lots of other cool stuff is from Chattanooga too! Win a care package full of random local stuff from Chattanooga, TN and the surrounding area. The higher the bid, the cooler the stuff.
\subsection{Crafty Care Package}
Katie (Rivard) Mazaitis (kathryn.mazaitis@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
A mystery multicraftual care package! May include: yarn, fiber, fabric, natural dyes, hand-patterned papers, collage notions, bath \& body treats, nice snacks. Exclusion requests accepted.
\subsection{Place to Stay in Chattanooga}
Erika Swartz '12 (erika.swartz@gmail.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
Come visit Outside Online's 2015 Best Town Ever! It's still pretty cool in 2017, even if it is a 16 hr drive from Olin. I'll put you up in my centrally located apartment downtown, with room to sleep 2 - 4 people. 

Chattanooga is a great destination for anyone interested in climbing (sport, trad, bouldering), mountain biking, trail running, or whitewater kayaking. If it's climbing you're into, I can hook you up with all the local beta, crashpads, and guidebooks during your stay. Meryl Stark '12 lives in town and can hook you up with any and all needed info on whitewater kayaking.
\subsection{Souvenir from a SCOPE Trip to the UK}
TOCA Design (brett.atkinson@students.olin.edu) \\
Starting Bid: \$5 \\
Winner(s): 
Top 2 bids\newline
The Tata Motors | Autodesk SCOPE team will buy you a gift on our next trip to England! The bigger the bid, the bigger the gift (maybe) (size or monetary value not specified).
\subsection{Lunch + AMA}
Matt Crawford '09 (mcrawford@7crawfords.com) \\
Starting Bid: \$5 \\
Winner(s): 
Top bidder\newline
I will take you to lunch at my favorite place in Needham, where we can talk about whatever you want.  Life advice, Olin advice, tales from the olde days, something I haven't thought of...

Includes transportation there and back for up to 3 guests and lunch for one.  Groups of up to 12 total (limited by the largest table there) are welcome, but you will have to arrange your own transportation.
\subsection{Take Byron \& Jones on an Indoor Walk!}
Byron \& Jones  (ashlee.talbot@olin.edu) \\
Starting Bid: \$8 \\
Winner(s): 
Top 2 bids\newline
There are cats on campus. These cats go on leaches. They love exploring and being around people. Should you win you will be given the option of walking Byron and Jones not once, not twice, but three times! This is an indoor walk (as being outside can get a bit complicated). Visit a lounge, take them to your room, travel up and down the stairs - it's up to you! (But actually, it's up to them, since cats tend to walk you). Toys and treats will be provided!
\subsection{2 Tix to my Next Show}
Brian Liebson (Brianliebson@gmail.com) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
I'm Brian, I'm an alumni. I graduated then joined the national tour of Cinderella the Musical as the fox! Now I'm auditioning, but I'll give you 2 tickets to the next show I'm in (that's convenient for you to get to). If they let me, I can bring you backstage and stuff too!
\subsection{It's Like Having Mom Here}
Financial Affairs Moms (vivian.glassman@olin.edu) \\
Starting Bid: \$10 \\
Winner(s): 
Top bidder\newline
Homesick?  Or maybe you just need a little extra TLC.  A group of Financial Affairs Moms are willing to adopt you for the rest of the school year.  We will send you 4 care packages at random times.  If you like we will send you an occasional card, and are willing to e-mail, text, or personally deliver words of encouragement (only with your consent).  Of course we might have to offer you the occasional Mom-ism or advice you don’t really want to hear, just to make the whole experience authentic.
\subsection{Red Ukulele }
Shyheim Russell (shyheim.russell@students.olin.edu) \\
Starting Bid: \$15 \\
Winner(s): 
Top bidder\newline
It's red, and its a mini guitar
\subsection{The Parcel B Secret You've Never Heard Of}
Sophia Nielsen (Sophia@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
It's no tree house but I can almost guarantee you've never heard of it.
\subsection{Play the Bagpipes}
Vienna Scheyer (vienna.scheyer@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
Hire me to play bagpipes at your event! If you give me enough notice, I can get a kilt and wear a uniform. I've been playing bagpipes for 5 years, and I can play requested tunes if they work on the bagpipes (if given notice).
\subsection{Piece of engineering history}
Michelle Davis (michelle.davis@olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top bidder\newline
Vintage Kueffel \& Esser Slide Rule with Leather Case
\subsection{Parcel B Adventure with Brennan and Walker}
Walker Trelease, Brennan Vandenhoek (walker@students.olin.edu) \\
Starting Bid: \$20 \\
Winner(s): 
Top 3 bids\newline
It will be a mystery until it happens. Trust us it will be worth it. Not for the faint of heart.
\subsection{ASL STEM Immersion Trip}
Mel Chua (mel@melchua.com) \\
Starting Bid: \$30 \\
Winner(s): 
Top bidder\newline
Ever wanted to experience engineering in a different language and culture without leaving the USA? Come hang out with Deaf engineers in Rochester at the National Technical Institute for the Deaf! No ASL knowledge required; we've got interpreters, keyboards, and notebooks and can teach you how to adapt to being "sign-impaired" if needed. Might be a particularly fun trip for those who work with the medical and/or disability community and want to see what it's like on the other side of things.

I (Mel) was the first deaf Olin student ('07) and a recent Olin postdoc, and am now a new RIT/NTID faculty member. I'll be your host into a world where sign language is normal and engineering faculty and students play with and question their relationships with assistive/adaptive technology on a daily basis. My research center is a product design group staffed entirely by d/Deaf and hard-of-hearing engineers (imagine "Deaf IDEO" and you'll be pretty close). Our city has the highest per capita Deaf population in the world, which means signing baristas, waiters who automatically write down the specials, and all sorts of lovely little tweaks in a world that's made with very different assumptions than the hearing norm. And now you, too, can experience an alternate engineering universe.

This item covers an all-expenses-paid trip to Rochester (you get yourself to/from Rochester we'll handle the rest) for up to 10 days for up to two people. Private guest room, real twin mattresses, and all the food and tea and coffee you want with any dietary needs accommodated. Scheduling done by mutual agreement. Airport pick-up included if needed, transit around the city available. Rochester is a 6-hour drive from Boston and has gorgeous hiking/lakes/beaches/etc. nearby, and these can easily be worked into your trip, with as much free/solo time as you want to have and automotive transit available if needed. I'll work with you to design a schedule around your interests and set up meetings/excursions/experiences with various people around town (Deaf science? Art? Theatre? Dance? You name it, we've got it). As a bonus, I'm also happy to teach cartooning, qualitative research methods, RSI prevention, and/or cooking, and can give plenty of advice on grad school and/or feedback on writing.

This item must be redeemed while I am working at RIT, which will be at least until August 2018, but may extend for longer.
\end{document}
